---
title: "STAT391Project"
author: "TaoZhang"
date: "2024-02-28"
output:
  pdf_document: default
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = FALSE)
```

```{r}
library(plyr)
library(dplyr)
library(tidyverse)
library(openintro)
library(alr4)
library (ggplot2)
library(ggpubr)
library(pROC)
```



```{r}
setwd("C:/Users/12068/OneDrive - UW/Desktop/UW Course/STAT423_hw/project")
data <- read.csv("heart_attack_prediction_dataset.csv")
```

Problem 2: At the 5 level of significance, is there a statistically significant association between heart attack risk and smoking, controlling for Diet?

```{r}
data1 <- data[, c("Smoking","Diet","Heart.Attack.Risk")]

head(data1)
```

```{r}
problem1_data1 <- data.frame(
    variable=c("heart attack risk", "smoking", "Alcohol.Consumption"), 
    type=c("Categorical", "Categorical", "Categorical"), 
    level=c("nomial", "nomial", "ordinal"),
  
    stringsAsFactors=FALSE)
print(problem1_data1)
table(data1$Heart.Attack.Risk)
table(data1$Smoking)
table(data1$Diet)
```
```{r}
data1$Heart.Attack.Risk <- revalue(as.factor(data1$Heart.Attack.Risk), 
                                c("1" = "risky", "0" = "not risky"))
data1$Smoking <- revalue(as.factor(data1$Smoking),
                      c("1" = "smoking", "0" = "not smoking"))
Health <- filter(data1, data1$Diet == "Healthy")
Average <- filter(data1, data1$Diet == "Average")
Unhealth <- filter(data1, data1$Diet == "Unhealthy")
p1 <-ggplot(Health, aes(x = Smoking, fill = Heart.Attack.Risk)) +
    labs(title = "Health",
         fill = "Heart.Attack.Risk",
         x = "Smoking",
         y = "") +
  geom_bar(position="fill")
p2 <-ggplot(Average, aes(x = Smoking, fill = Heart.Attack.Risk)) +
    labs(title = "Average Health",
         fill = "Heart.Attack.Risk",
         x = "Smoking",
         y = "") +
  geom_bar(position="fill")
p3 <-ggplot(Unhealth, aes(x = Smoking, fill = Heart.Attack.Risk)) +
    labs(title = "Unhealth",
         fill = "Heart.Attack.Risk",
         x = "Smoking",
         y = "") +
  geom_bar(position="fill")
ggarrange(p1,p2,p3,ncol = 1, nrow = 3)
```
It looks there is not a statistically significant association between heart attack risk and smoking, controlling for Diet.
Next, we calculate whether it's significant or not.






```{r}
table(data1$Heart.Attack.Risk, data1$Smoking, data1$Diet)
mantelhaen.test(data1$Heart.Attack.Risk, data1$Smoking, data1$Diet)
```

From Cochran Mantel Haenszel (CMH) Test, the p-value > 0.1, so we fail to reject the H_0 and there is not a sufficient evidence to support that Diet is  not a confounding variable.

```{r}
Healthy_chi <- chisq.test(Health$Heart.Attack.Risk, Health$Smoking)
Healthy_chi

Average_chi <- chisq.test(Average$Heart.Attack.Risk, Average$Smoking)
Average_chi

unhealthy_chi <- chisq.test(Unhealth$Heart.Attack.Risk, Unhealth$Smoking)
unhealthy_chi
```

##### Healthy diet
H_0: there is no association between variables smoking and Heart.Attack.Risk among Healthy diet people. 
H_a: there is an association between variables smoking and Heart.Attack.Risk among Healthy diet people. 

In Healthy diet people sample, from chi-squared test, since p-value > 0.1, so we fail to reject the H_0 and there is not a sufficient evidence to support that there is an association between variables smoking and Heart.Attack.Risk. 


##### Healthy diet
H_0: there is no association between variables smoking and Heart.Attack.Risk among Average Healthy diet people. 
H_a: there is an association between variables smoking and Heart.Attack.Risk among Average Healthy diet people. 

In Average Healthy diet people sample, from chi-squared test, since p-value > 0.1, so we fail to reject the H_0 and there is not a sufficient evidence to support that there is an association between variables smoking and Heart.Attack.Risk. 


##### Healthy diet
H_0: there is no association between variables smoking and Heart.Attack.Risk among unhealthy diet people. 
H_a: there is an association between variables smoking and Heart.Attack.Risk among unhealthy diet people. 
In unhealthy diet people sample, from chi-squared test, since p-value > 0.1, so we fail to reject the H_0 and there is not a sufficient evidence to support that there is an association between variables smoking and Heart.Attack.Risk. 


```{r}
head(data)
```


Problem 3:

```{r}
data$AgeGroup <- cut(data$Age, breaks=4, labels=c("Youth", "Young Adult", "Middle Aged", "Senior"))
data$HeartRateGroup <- cut(data$Heart.Rate, breaks=4, labels=c("Low", "Medium", "High", "Very High"))
data$ExerciseHoursGroup <- cut(data$Exercise.Hours.Per.Week, breaks=4, labels=c("Sedentary", "Light", "Moderate", "Active"))

ggplot(data, aes(x=AgeGroup, y=Heart.Attack.Risk, fill=AgeGroup)) +
  geom_bar(stat="summary", fun=mean) +
  ggtitle("Heart Attack Risk by Age Group") +
  xlab("Age Group") +
  ylab("Average Heart Attack Risk")


ggplot(data, aes(x=HeartRateGroup, y=Heart.Attack.Risk, fill=HeartRateGroup)) +
  geom_bar(stat="summary", fun=mean) +
  ggtitle("Heart Attack Risk by Heart Rate Group") +
  xlab("Heart Rate Group") +
  ylab("Average Heart Attack Risk")

ggplot(data, aes(x=ExerciseHoursGroup, y=Heart.Attack.Risk, fill=ExerciseHoursGroup)) +
  geom_bar(stat="summary", fun=mean) +
  ggtitle("Heart Attack Risk by Exercise Hours Group") +
  xlab("Exercise Hours Group") +
  ylab("Average Heart Attack Risk")

ggplot(data, aes(x=factor(Heart.Attack.Risk), y=Age)) +
  geom_boxplot() +
  ggtitle("Age Distribution by Heart Attack Risk") +
  xlab("Heart Attack Risk") +
  ylab("Age")

ggplot(data, aes(x=factor(Heart.Attack.Risk), y=Heart.Rate)) +
  geom_boxplot() +
  ggtitle("Heart Rate Distribution by Heart Attack Risk") +
  xlab("Heart Attack Risk") +
  ylab("Heart Rate")

ggplot(data, aes(x=factor(Heart.Attack.Risk), y=Exercise.Hours.Per.Week)) +
  geom_boxplot() +
  ggtitle("Exercise Hours Per Week Distribution by Heart Attack Risk") +
  xlab("Heart Attack Risk") +
  ylab("Exercise Hours Per Week")
```














Problem 4:
```{r}
data <- read.csv("heart_attack_prediction_dataset.csv")
model1 <- glm(as.factor(Heart.Attack.Risk) ~ Age + Sex+ Cholesterol+ Heart.Rate+Diabetes+Family.History+Smoking+  Obesity + Alcohol.Consumption + Exercise.Hours.Per.Week + Stress.Level + Income + BMI + Triglycerides + Country,
                      data = data,
                      family = binomial)

summary(model1)
```

```{r}
model2 = glm(as.factor(Heart.Attack.Risk) ~  Obesity + Alcohol.Consumption +Exercise.Hours.Per.Week+Stress.Level+Income+BMI+Triglycerides, data = data, family = binomial)
anova(model1, model2,  test = "Chisq")
```

```{r}
head(data)
```


```{r}
plot(model1)
```





```{r}
# 预测概率，并基于0.5阈值进行分类
```


```{r}
data$predicted_probabilities <- predict(model1, data, type="response")
data$prediction <- ifelse(data$predicted_probabilities >= 0.5, 1, 0)

# 创建两个新的数据框：一个用于成功预测，另一个用于不成功预测
success <- data[data$Heart.Attack.Risk == data$prediction, ]
not_success <- data[data$Heart.Attack.Risk != data$prediction, ]
```


```{r}
```


```{r}
boxplot(data$predicted_probabilities)
```


```{r}
model1 <- glm(as.factor(Heart.Attack.Risk) ~ Age + Sex+ Cholesterol+ Heart.Rate+Diabetes+Family.History+Smoking+  Obesity + Alcohol.Consumption + Exercise.Hours.Per.Week + Stress.Level + Income + BMI + Triglycerides + Country,
                      data = success,
                      family = binomial)
summary(model1)
```






```{r}
predicted_probabilities <- predict(model1, data, type = "response")

roc_obj <- roc(data$Heart.Attack.Risk, predicted_probabilities)

plot(roc_obj, main="ROC Curve", col="#1c61b6", lwd=2)
abline(a=0, b=1, col="red")

auc(roc_obj)
```










